% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}



\begin{document}

\title{Non-Parametric Analysis of Social Influence Bias in the California Report Card}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%

% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
\textbf{ TODO }
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\input{introduction.tex}

\section{Related Work}
Human opinion and rating in the presence of social influence has been
well studied. In Asch's famous conformity experiments, participants were asked to match a line with a set of three three disparate lines, after 0 to 16 confederates had first given a unanimous incorrect answer. On average, 25\% of participants conformed to the incorrect consensus. In 2011, Lorenz et. al described how social influence can undermine the effectiveness of crowd intelligence in estimation tasks. In particular, they describe social influence effect as causing a diminishment in diversity of opinion without improvement of its collective error. 

Extending the study of social influence to online recommendation systems, Danescu-Niculescu-Mizil et. al's case study of Amazon helpfulness reviews argues that a written review's perceived helpfulness depends not just on the content of the review, but also the its score's relation to other scores. In order to better distinguish social influence from uninfluenced agreement, Muchnik et. al designed a randomized experiment in which comments were randomly up-treated or down-treated. Their work concluded a asymmetric herding effect, with a tendency towards positive bias. Sipos et. al argue that context along with an aggregate rating plays a large role in the users' ratings. That is, users may attempt to “correct" the average, by voting in a more polarizing manner (more positively or negatively).

The CRC presents a particular form of social influence in that the median grade is revealed after the user has adjusted the slider, and then given an opportunity to change. Zhu et. al examined a similar phenomenon in their experiment in which users rate their preference of an image, which was followed (either immediately or later) by a presentation of the crowd consensus opinion. Users were given an opportunity to change their response. Their work concluded the influence of conformity pressures is strongest, among other factors, when users are required to make their second decision sometime later, rather than immediately afterwards.


\input{crc_description.tex}
\input{significance_model.tex}
\input{path_model.tex}
\input{change_model.tex}
\input{results.tex}
\input{conclusion.tex}
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}


%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}

\balancecolumns
% That's all folks!
\end{document}
